Testing atlantisom: generate survey sampled length comps

### 2019-05-13 StdSurvLengthCompTest.Rmd
initial standard survey length sampling

---
title: "Testing atlantisom: generate standard survey length and age comps"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

initCCA <- FALSE
initNEUS <- TRUE
initNOBA <- FALSE

if(initCCA){
  d.name <- here("atlantisoutput","CalCurrentSummitScenario1")
  functional.groups.file <- "CalCurrentV3Groups.csv"
  biomass.pools.file <- "DIVCalCurrentV3_BIOL.nc"
  biol.prm.file <- "CalCurrentV3_Biol.prm"
  box.file <- "CalCurrentV3_utm.bgm"
  initial.conditions.file <- "DIVCalCurrentV3_BIOL.nc"
  run.prm.file <- "CalCurrentV3_run.xml"
  scenario.name <- "CCV3"
}

if(initNEUS){
  d.name <- here("atlantisoutput","NEUStest20160303")
  functional.groups.file <- "NeusGroups.csv" 
  biomass.pools.file <- ""
  biol.prm.file <- "at_biol_neus_v15_DE.prm"
  box.file <- "neus30_2006.bgm"
  initial.conditions.file <- "inneus_2012.nc"
  run.prm.file <- "at_run_neus_v15_DE.xml"
  scenario.name <- "neusDynEffort_Test1_"
}

if(initNOBA){
  d.name <- here("atlantisoutput","NOBACERESGlobalSustainability")
  functional.groups.file <- "nordic_groups_v04.csv" 
  biomass.pools.file <- "nordic_biol_v23.nc"
  biol.prm.file <- "nordic_biol_incl_harv_v_007_3.prm"
  box.file <- "Nordic02.bgm"
  initial.conditions.file <- "nordic_biol_v23.nc"
  run.prm.file <- "nordic_run_v01.xml"
  scenario.name <- "nordic_runresults_01"
}
# NOBA note: output filenames in CCA and NEUS begin with "output" and the run_truth function is written to expect this. Need to check if default Atlantis output file nomenclature has changed or if NOBA is a special case. For now, NOBA filenames have been changed to include prefix "output"
```

@@

if(initCCA) {
  d.name <- here("atlantisoutput","CalCurrentSummitScenario1")
  truth.file <- "outputCCV3run_truth.RData"
  load(file.path(d.name, truth.file))
  CCAresults <- result
}

if(initNEUS) {
  d.name <- here("atlantisoutput","NEUStest20160303")
  truth.file <- "outputneusDynEffort_Test1_run_truth.RData" 
  load(file.path(d.name, truth.file))
  NEUSresults <- result
}

if(initNOBA){
  d.name <- here("atlantisoutput","NOBACERESGlobalSustainability")
  truth.file <- "outputnordic_runresults_01run_truth.RData" 
  load(file.path(d.name, truth.file))
  NOBAresults <- result
}

@@

<!--We can also read in previously generated survey census files based on true biomass results for comparison if necessary, but not yet used here (see [TrueBioTest](https://sgaichas.github.io/poseidon-dev/TrueBioTest.html).)

```{r readsurvey1, eval=FALSE}

if(initCCA) {
  CCAsurveyB_frombio <- readRDS(file.path(d.name, paste0(scenario.name, "surveyBcensus.rds")))
}

if(initNEUS) {
  NEUSsurveyB_frombio <- readRDS(file.path(d.name, paste0(scenario.name, "surveyBcensus.rds")))
}

if(initNOBA) {
  NOBAsurveyB_frombio <- readRDS(file.path(d.name, paste0(scenario.name, "surveyBcensus.rds")))
}

```
-->

## Simulate a survey part 3: sample for length and age composition

Here we will compare the effects of survey timing, spatial coverage, and survey selectivity on the sampled (cohort) age comps. This section uses the `atlantisom::create_survey()` and `atlantisom::sample_fish()` to get a biological sample dataset. From that dataset, several other functions can be run:

 *  age samples from sample_ages
 *  length samples from sample_lengths (TO BE WRITTEN)
 *  weight samples from sample_weights (TO BE WRITTEN)
 *  diet samples from sample_diet

To create a survey, the user specifies the timing of the survey, which species are captured, the spatial coverage of the survey, the species-specific survey efficiency ("q"), and the selectivity at age for each species.

The following settings should achieve a survey that samples all Atlantis model output timesteps, all fish and shark species, and all model polygons, with perfect efficiency and full selectivity for all ages:

```{r census-spec, message=FALSE, warning=FALSE}

# should return a perfectly scaled survey 
effic1 <- data.frame(species=funct.group.names,
                     efficiency=rep(1.0,length(funct.group.names)))

# should return all lengths fully sampled (Atlantis output is 10 age groups per spp)
# BUT CHECK if newer Atlantis models can do age-specific outputs
selex1 <- data.frame(species=rep(funct.group.names, each=10),
                     agecl=rep(c(1:10),length(funct.group.names)),
                     selex=rep(1.0,length(funct.group.names)*10))

# should return all model areas
boxpars <- load_box(d.name, box.file)
boxall <- c(0:(boxpars$nbox - 1))

# these are model specific, generalized above
# if(initCCA) boxall <- c(0:88) 
# if(initNEUS) boxall <- c(0:29)
# if(initNOBA) boxall <- c(0:59)

# should return all model output timesteps; need to generalize
# if(initCCA) timeall <- c(0:100) 
# if(initNEUS) timeall <- c(0:251)
# if(initNOBA) timeall <- c(0:560)

# generalized
runpar <- load_runprm(d.name, run.prm.file)
noutsteps <- runpar$tstop/runpar$outputstep
stepperyr <- if(runpar$outputstepunit=="days") 365/runpar$toutinc

timeall <- c(0:noutsteps)

# define set of species we expect surveys to sample (e.g. fish only? vertebrates?)
# for ecosystem indicator work test all species, e.g.
survspp <- funct.group.names

# to keep plots simpler, currently hardcoded for vertebrate/fished invert groups
# if(initCCA) survspp <- funct.group.names[c(1:44, 59:61, 65:68)] 
# if(initNEUS) survspp <- funct.group.names[1:21]
# if(initNOBA) survspp <- funct.group.names[1:36]

# for length and age groups lets just do fish and sharks
# NOBA model has InvertType, changed to GroupType in file, but check Atlantis default
if(initNOBA) funct.groups <- rename(funct.groups, GroupType = InvertType)

@@

#if(initCCA) survspp <- survspp[!survspp %in% "Pisciv_T_Fish"]

Here we use `create_survey` on the numbers output of `run_truth` to create the survey census of age and length composition.

```{r censusNbased}

# this uses result$nums, but we are not creating a biomass index this time, so we don't need a weight at age conversion

if(initCCA) datN <- CCAresults$nums
if(initNEUS) datN <- NEUSresults$nums
if(initNOBA) datN <- NOBAresults$nums

survey_testNall <- create_survey(dat = datN,
                                 time = timeall,
                                 species = survspp,
                                 boxes = boxall,
                                 effic = effic1,
                                 selex = selex1)

Next, get true annual (cohort) age comp from this census survey based on run truth. (is there a standard Atlantis output I can compare this to as we did for biomass?)

```{r truecohortagecomp}
# what is true composition? need annual by species, use code from sample_fish
# do tidyly
dat2 <- survey_testNall %>%
  group_by(species, agecl, time) %>%
  summarize(numAtAge = sum(atoutput))

#dat<-survey_testNall
#dat2 <- aggregate(dat$atoutput,list(dat$species,dat$agecl,dat$time),sum)
#names(dat2) <- c("species","agecl","time","numAtAge")

totN <- dat2 %>%
  group_by(species, time) %>%
  summarize(totN = sum(numAtAge))

#totN <- aggregate(dat2$numAtAge,list(dat2$species,dat2$time),sum )
#names(totN) <- c("species","time","totN")

dat2totN <- merge(dat2, totN)

# ageclcomp <- ggplot(dat2totN, aes(x=agecl, y=numAtAge/totN, col=time)) +
#   geom_point()
# 
# ageclcomp + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 1, scales="free")
# ageclcomp + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 2, scales="free")
# ageclcomp + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 3, scales="free")
# ageclcomp + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 4, scales="free")
# ageclcomp + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 5, scales="free")

We know from the previous test that the `sample_fish` function with the maximum possible effective sample size compares favorably (or perfectly) to true annual age comp calculated above as a test. Now we examine the effects of changing survey timing, survey area, survey selectivity, and fish sample size on age comps.

The standard survey approach is described [here](https://sgaichas.github.io/poseidon-dev/StandardSurveyTest.html). First, we map species into general groups for each model:

# make defaults that return a standard survey, implement in standard_survey
# users need to map their species groups into these general ones
#   large pelagics/reef associated/burrowers/otherwise non-trawlable
#   pelagics
#   demersals
#   selected flatfish

@@

We use the following specifications for our default standard bottom trawl survey, including survey cv by species group:

@@

# general specifications for bottom trawl survey, with items defined above commented out to avoid wasting time loading already loaded files:
#   once per year at mid year
#   could generalize from the run.prm file: 
# runpar <- load_runprm(d.name, run.prm.file)
# noutsteps <- runpar$tstop/runpar$outputstep
# stepperyr <- if(runpar$outputstepunit=="days") 365/runpar$toutinc
#   take midpoint of 0, steps per year to start seq and go to max time by steps per year
midptyr <- round(median(seq(1,stepperyr)))

@@

#   ~75-80% of boxes (leave off deeper boxes?)
# boxpars <- load_box(d.name, box.file)
boxsurv <- c(2:round(0.8*(boxpars$nbox - 1)))

@@

This generates the standard survey once per year, most areas, with mixed efficiency and selectivity.

@@

# this uses result$nums, but we are not creating a biomass index this time, so we don't need a weight at age conversion

if(initCCA) datN <- CCAresults$nums
if(initNEUS) datN <- NEUSresults$nums
if(initNOBA) datN <- NOBAresults$nums

survey_testNstd <- create_survey(dat = datN,
                                 time = annualmidyear,
                                 species = survspp,
                                 boxes = boxsurv,
                                 effic = efficmix,
                                 selex = selexmix)

# consider saving this interim step if it takes a long time to generate

@@

Now we sample fish with no error from the standard survey:

```{r comptest1, message=FALSE, warning=FALSE}
# setting the effN higher than actual numbers results in sampling all

# this one is high but not equal to total for numerous groups
effNhigh <- data.frame(species=survspp, effN=rep(1e+8, length(survspp)))

comptesthigh <- sample_fish(survey_testNstd, effNhigh)
names(comptesthigh) <- c("species","agecl","polygon", "layer","time","numAtAgesamp")

comptesttot <- aggregate(comptesthigh$numAtAgesamp,list(comptesthigh$species,comptesthigh$time),sum )
names(comptesttot) <- c("species","time","totsamp")

comptestprop <- merge(comptesthigh, comptesttot)
```

And compare this to the true age comp above to see the impact of only standard survey sampling on age comps:

```{r comptest1plot, message=FALSE, warning=FALSE}

# compare individual years, these proportions at age should not match
comparecomps <- ggplot() +
  geom_point(data=subset(dat2totN, time==min(annualmidyear)), aes(x=agecl, y=numAtAge/totN, color="true"), alpha = 0.3) +
  geom_point(data=subset(comptestprop, time==min(annualmidyear)), aes(x=agecl, y=numAtAgesamp/totsamp, color="samp"), alpha = 0.3) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=paste0(scenario.name, " start"))

comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 1, scales="free")
comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 2, scales="free")
comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 3, scales="free")
if(initCCA) comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 4, scales="free")
#comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 5, scales="free")

comparecomps <- ggplot() +
  geom_point(data=subset(dat2totN, time==annualmidyear[length(annualmidyear)/2]), aes(x=agecl, y=numAtAge/totN, color="true"), alpha = 0.3) +
  geom_point(data=subset(comptestprop, time==annualmidyear[length(annualmidyear)/2]), aes(x=agecl, y=numAtAgesamp/totsamp, color="samp"), alpha = 0.3)+
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=paste0(scenario.name, " midpoint"))

comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 1, scales="free")
comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 2, scales="free")
comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 3, scales="free")
if(initCCA) comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 4, scales="free")
#comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 5, scales="free")

comparecomps <- ggplot() +
  geom_point(data=subset(dat2totN, time==annualmidyear[length(annualmidyear)]), aes(x=agecl, y=numAtAge/totN, color="true"), alpha = 0.3) +
  geom_point(data=subset(comptestprop, time==annualmidyear[length(annualmidyear)]), aes(x=agecl, y=numAtAgesamp/totsamp, color="samp"), alpha = 0.3)+
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=paste0(scenario.name, " end"))

comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 1, scales="free")
comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 2, scales="free")
comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 3, scales="free")
if(initCCA) comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 4, scales="free")
#comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 5, scales="free")

@@

Now we run `sample_fish` with a more realistic biological sample size for each species, to see the combined impact of the standard survey and biological sampling:

```{r comptest2, message=FALSE, warning=FALSE}
# sample_fish uses an effN effective sample size for multinomial
# but this should be the REAL sample size taken (annual average over whole area)
# sample size of fish for lengths--a fairly large number
# a proportion of this is used for ages below
# assign by groups as above

@@

comptestmix <- sample_fish(survey_testNstd, effNmix)
names(comptestmix) <- c("species","agecl","polygon", "layer","time","numAtAgesamp")

comptestmixtot <- aggregate(comptestmix$numAtAgesamp,list(comptesthigh$species,comptesthigh$time),sum )
names(comptestmixtot) <- c("species","time","totsamp")

comptestmixprop <- merge(comptestmix, comptestmixtot)

@@

We can compare true (cohort) age comp ("true"), survey sampled age comp with no subsampling effect ("samphigh"), and age comp from biological subsamling aboard the survey ("sampreal"):

```{r comptest12plot, message=FALSE, warning=FALSE}

# compare individual years, these proportions at age wont match
comparecomps <- ggplot() +
  geom_point(data=subset(dat2totN, time==min(annualmidyear)), aes(x=agecl, y=numAtAge/totN, color="true"), alpha = 0.3) +
  geom_point(data=subset(comptestprop, time==min(annualmidyear)), aes(x=agecl, y=numAtAgesamp/totsamp, color="samphigh"), alpha = 0.3) +
  geom_point(data=subset(comptestmixprop, time==min(annualmidyear)), aes(x=agecl, y=numAtAgesamp/totsamp, color="sampreal"), alpha = 0.3) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=paste0(scenario.name, " start"))

comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 1, scales="free")
comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 2, scales="free")
comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 3, scales="free")
if(initCCA) comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 4, scales="free")
#comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 5, scales="free")

#ggsave("stdsurvcomp_realeffN_time0.png", width=11, height=11)

comparecomps <- ggplot() +
  geom_point(data=subset(dat2totN, time==annualmidyear[length(annualmidyear)/2]), aes(x=agecl, y=numAtAge/totN, color="true"), alpha = 0.3) +
  geom_point(data=subset(comptestprop, time==annualmidyear[length(annualmidyear)/2]), aes(x=agecl, y=numAtAgesamp/totsamp, color="samphigh"), alpha = 0.3) +
  geom_point(data=subset(comptestmixprop, time==annualmidyear[length(annualmidyear)/2]), aes(x=agecl, y=numAtAgesamp/totsamp, color="sampreal"), alpha = 0.3) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=paste0(scenario.name, " midpoint"))

comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 1, scales="free")
comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 2, scales="free")
comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 3, scales="free")
if(initCCA) comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 4, scales="free")
#comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 5, scales="free")

#ggsave("stdsurvcomp_realeffN_time100.png", width=11, height=11)

comparecomps <- ggplot() +
  geom_point(data=subset(dat2totN, time==annualmidyear[length(annualmidyear)]), aes(x=agecl, y=numAtAge/totN, color="true"), alpha = 0.3) +
  geom_point(data=subset(comptestprop, time==annualmidyear[length(annualmidyear)]), aes(x=agecl, y=numAtAgesamp/totsamp, color="samphigh"), alpha = 0.3) +
  geom_point(data=subset(comptestmixprop, time==annualmidyear[length(annualmidyear)]), aes(x=agecl, y=numAtAgesamp/totsamp, color="sampreal"), alpha = 0.3) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=paste0(scenario.name, " end"))

comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 1, scales="free")
comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 2, scales="free")
comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 3, scales="free")
if(initCCA) comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 4, scales="free")
#comparecomps + facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 5, scales="free")

#ggsave("stdsurvcomp_realeffN_time250.png", width=11, height=11)

@@

With these biological sample sizes (~1000 fish per year in the whole area) the impact of biological subsampling is minimal compared with the impact of survey length selectivity. Smaller biological sample sizes (~25 fish per year for nontrawl category) show more difference from the survey sampled age comp.

>>>>

---
title: "Testing atlantisom: generate survey sampled length comps"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

initCCA <- TRUE
initNEUS <- FALSE
initNOBA <- FALSE

if(initCCA) source(here("config/CCConfig.R"))

if(initNEUS) source(here("config/NEUSConfig.R"))

if(initNOBA) source(here("config/NOBAConfig.R"))

@@

if(initCCA) {
  truth.file <- "outputCCV3run_truth.RData"
  load(file.path(d.name, truth.file))
  truth <- result
}

if(initNEUS) {
  truth.file <- "outputneusDynEffort_Test1_run_truth.RData" 
  load(file.path(d.name, truth.file))
  truth <- result
}

if(initNOBA){
  truth.file <- "outputnordic_runresults_01run_truth.RData" 
  load(file.path(d.name, truth.file))
  truth <- result
}

@@

## Simulate a survey part 4: sample for length composition

This section uses the `atlantisom::create_survey()` and `atlantisom::sample_fish()` to get a biological sample dataset. From that dataset, several other functions can be run:

 *  age samples from `calc_stage2age` and `sample_ages`
 *  length samples from `calc_age2length` and `sample_lengths` (TO BE WRITTEN)
 *  weight samples from `calc_age2length` and`sample_weights` (TO BE WRITTEN)
 *  diet samples from `sample_diet`

Atlantis outputs numbers by cohort (stage-age) and growth informtation, but does not output size of animals directly. The function we are testing here, `atlantisom::calc_age2length` converts numbers by cohort to a length composition. The [workflow originally envisioned](https://onedrive.live.com/?authkey=%21AFQkOoKRz64TLUw&cid=59547B4CB95EF108&id=59547B4CB95EF108%216291&parId=59547B4CB95EF108%216262&o=OneUp) was to create a survey, sample fish from the survey, then apply this function. We determined that it will not work better to create a length comp for the whole population, which could then be sampled. We rethought what we needed [here](https://sgaichas.github.io/poseidon-dev/RethinkSamplingFunctions.html) and test the new functions in this document.

### Standard survey settings for testing 
To create a survey, the user specifies the timing of the survey, which species are captured, the spatial coverage of the survey, the species-specific survey efficiency ("q"), and the selectivity at age for each species.

# make defaults that return a standard survey, implement in standard_survey
# users need to map their species groups into these general ones
#   large pelagics/reef associated/burrowers/otherwise non-trawlable
#   pelagics
#   demersals
#   selected flatfish
if(initNOBA) funct.groups <- rename(funct.groups, GroupType = InvertType)

@@

@@

The following settings are for our example standard survey once per year, most areas, with mixed efficiency and selectivity:

@@

# general specifications for bottom trawl survey, with items defined above commented out to avoid wasting time loading already loaded files:
#   once per year at mid year
# generalized timesteps all models
runpar <- load_runprm(d.name, run.prm.file)
noutsteps <- runpar$tstop/runpar$outputstep
stepperyr <- if(runpar$outputstepunit=="days") 365/runpar$toutinc

midptyr <- round(median(seq(1,stepperyr)))

@@

#   ~75-80% of boxes (leave off deeper boxes?)
boxpars <- load_box(d.name, box.file)
boxsurv <- c(2:round(0.8*(boxpars$nbox - 1)))

@@

Here we use `create_survey` on the numbers output of `run_truth` to create the survey census of age composition.

@@

survey_testNstd <- create_survey(dat = truth$nums,
                                 time = annualmidyear,
                                 species = survspp,
                                 boxes = boxsurv,
                                 effic = efficmix,
                                 selex = selexmix)

@@

Next we apply the aggregateDensityData function can to resn and structn for survey times, species, and boxes.

```{r aggdens}

# aggregate true resn per survey design
survey_aggresnstd <- aggregateDensityData(dat = truth$resn,
                                 time = annualmidyear,
                                 species = survspp,
                                 boxes = boxsurv)

# aggregate true structn per survey design
survey_aggstructnstd <- aggregateDensityData(dat = truth$structn,
                                 time = annualmidyear,
                                 species = survspp,
                                 boxes = boxsurv)

@@

Now we should have inputs to `sample_fish` on the same scale, and they need to be aggregated across boxes into a single biological sample for the whole survey. The `sample_fish` applies the median for aggregation and does not apply multinomial sampling if `sample=FALSE` in the function call.

```{r stdsurvey-lensamp, warning=FALSE, message=FALSE}

@@

# apply default sample fish as before to get numbers
numsstd <- sample_fish(survey_testNstd, effNmix)

#dont sample these, just aggregate them using median (effNmix does nothing)
structnstd <- sample_fish(survey_aggstructnstd, effNmix, sample = FALSE)

resnstd <-  sample_fish(survey_aggresnstd, effNmix, sample = FALSE)
```

```{r stdsurvey-calcage2length, warning=FALSE, message=FALSE}

# now cut these down to a single species for testing

atf_numsstd <- numsstd[numsstd$species == "Arrowtooth_flounder",]
atf_structnstd <- structnstd[structnstd$species == "Arrowtooth_flounder",]
atf_resnstd <- resnall[resnstd$species == "Arrowtooth_flounder",]

atf_length_stdsurv <- calc_age2length(structn = atf_structnstd,
                                 resn = atf_resnstd,
                                 nums = atf_numsstd,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

@@

Plot samples one species:

```{r atflengthsamp1-test}

lfplot <- ggplot(atf_length_stdsurv$natlength, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte()

lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 1, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 2, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 3, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 4, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 5, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 6, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 7, scales="free_y")

# try dir = "v" option for vertical lf comparisons

@@

## Samples for all species, then SAVE

Now run for all species in the survey.

```{r allspplengthsamp}

length_stdsurv <- calc_age2length(structn = structnstd,
                                 resn = resnstd,
                                 nums = numsstd,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

#save for later use, takes a long time to generate
saveRDS(length_stdsurv, file.path(d.name, paste0(scenario.name, "length_stdsurv.rds")))

Runtime for census lengths was 5.5 hours for CCA. For standard survey lengths runtime was not reduced because the dimensions (species, timesteps) were identical.

Compare sampled lf with census from [here](https://sgaichas.github.io/poseidon-dev/CCATrueLengthCompTest.html):

```{r loadlengthcomp, echo=TRUE, eval=FALSE}

length_censussurvsamp <- readRDS(file.path(d.name, paste0(scenario.name, "length_censussurvsamp.rds")))

length_stdsurv <- readRDS(file.path(d.name, paste0(scenario.name, "length_stdsurv.rds")))

Comparison plots for other species:

```{r moreplots, echo=TRUE, eval=FALSE}

ss_length_censussurvsamp <- length_censussurvsamp$natlength %>%
  filter(species == "Herring")

ss_length_stdsurv <- length_stdsurv$natlength %>%
  filter(species == "Herring")

# add sample, this is census, probably want it first?
lfplot <- ggplot(ss_length_censussurvsamp, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte()

lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 1, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 2, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 3, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 4, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 5, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 6, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 7, scales="free_y")
